### 2021-08-13 content/80.formal-definition.tex

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or \href{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html#contextual-vs-data-entities}{both}; and must be typed with at least one $Class(e)$.

>>>>

The concept of an $Entity(e)$ is introduced as being either a $DataEntity(e)$, a $ContextualEntity(e)$, or both\footnote\url{https://www.researchobject.org/ro-crate/1.1/contextual-entities.html#contextual-vs-data-entities}}; and must be typed with at least one $Class(e)$.
